### 2017-04-01 paper/sections/Formalization.tex
changes..
A bit.
minor changes
Fix.

\begin{figure*}[htbp]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \\
\text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
\text{\red{Values}}       & v & \Coloneqq & <I>\new{C}
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax.}\label{fig:syntax}
\end{figure*}

@@

\subsubsection{\mbody}
\begin{mathpar}
	\inferrule* [left=]
	{C \{ m() \; \kwoverride \; C ... \} }
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}

	\inferrule* [left=]
	{C \{ m() \; \kwoverride \; A ... \} }
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}

	\inferrule* [left=]
	{   \mbody(m, C) = \{ A.m(), B.m(), ...\}
		\\ \nexists \; C.m()}
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } A}
\end{mathpar}

$$\interface{I}{I}{M}$$

$mbody(m, I)$ algorithm:
\begin{itemize}
	\item If m is defined in I directly, then return I.m()
	\item Else, let $\overline{I'} = mdefined(fathers(I))$, all ancestors of $I$ that has directly defined $m()$.
	\item $\overline{I''} = needed(\overline{I'})$, keep only interfaces that are needed, which are not super-interface of others.
	\item If $\overline{I''}$ is unique, then return this unique one. Else if any two I1,I2 in $\overline{I''}$ share a parent in $\overline{I'}$, then diamond conflict is detected, report error. Else return multiple $m()$s.
\end{itemize}

@@

>>>>

\begin{figure*}[htbp]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \\
\text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
\text{\red{Values}}       & v & \Coloneqq & <J>\new{I}
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax.}\label{fig:syntax}
\end{figure*}

@@

\subsubsection{\mbody}
\begin{mathpar}	
	\inferrule* [left=]
	{  \mostSpecific(m, I_d, I_s) = \{I\} \\
		\mostSpecific_3(m, I_d, I) = \{J\} \\
		\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{E}{m}{X}{x}{I}{e_0}...\}}
	{\mbody(m, I_d, I_s) = (\overline{X} \; \overline{x}, E \; e_0)}
\end{mathpar}

\begin{comment}
$mbody(m, I)$ algorithm:
\begin{itemize}
	\item If m is defined in I directly, then return I.m()
	\item Else, let $\overline{I'} = mdefined(fathers(I))$, all ancestors of $I$ that has directly defined $m()$.
	\item $\overline{I''} = needed(\overline{I'})$, keep only interfaces that are needed, which are not super-interface of others.
	\item If $\overline{I''}$ is unique, then return this unique one. Else if any two I1,I2 in $\overline{I''}$ share a parent in $\overline{I'}$, then diamond conflict is detected, report error. Else return multiple $m()$s.
\end{itemize}
\end{comment}

\subsubsection{\mostSpecific}
\begin{mathpar}	
	\inferrule* [left=]
	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
			\end{tabular}}\right.}

	\inferrule* [left=]
	{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
	{\mostSpecific_2(m, I) = prune(set)}

	\inferrule* [left=]
	{ set = \; $\{$ K <: J \; $and$ \; K \neq J \; $and$ \; K >: I \; | \\
		\kwinterface \; K \; \kwextends \; \overline{K} \; \{ E \; m(\overline{X} \; \overline{x}) \;
		\kwoverride \; J ... \}  $\}$ }
	{\mostSpecific_3(m, I, J) = prune(set)}
\end{mathpar}

$$ prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \} $$

@@

\subsection{\pathcheck}
$$\forall P \in getSupTypes(I)$$

\begin{align*}
 set = \{ class | class \in getSupTypes(I) 
		\\ class.m \text{ defined in its body }
		\\ class <: P \}
\end{align*}

$$ prune(set) = \{x \in set | \nexists y \in set, y <: x, y \neq x \} $$
$$ |prune(set)| <= 1 $$
